Efficient High-Level Abstractions for Web Programming

### 2013-09-10 papers/gpce2013/gpce2013.tex
more precise indications to find the code of chooze

Chooze~\footnote{Source code is available at
\href{http://github.com/julienrf/chooze}{http://github.com/julienrf/chooze}} is an existing
complete application for making polls. It allows users to create a poll, define the choice
alternatives, share the poll, vote and look at the results. It contains JavaScript code to handle
the dynamic behavior of the application: double-posting prevention, dynamic form update and rich
interaction with the document. The size of the whole application (server and client sides) is about one thousand lines of code.

>>>>

Chooze~\footnote{Source code is available at
\href{http://github.com/julienrf/chooze}{http://github.com/julienrf/chooze}, under the branches \code{vanilla}, \code{jquery}, \code{gwt}, \code{haxe} and \code{js-scala}} is an existing
complete application for making polls. It allows users to create a poll, define the choice
alternatives, share the poll, vote and look at the results. It contains JavaScript code to handle
the dynamic behavior of the application: double-posting prevention, dynamic form update and rich
interaction with the document. The size of the whole application (server and client sides) is about one thousand lines of code.
